The natural history of scavenging in vertebrates

### 2016-03-22 natural history of scavenging.tex
tidied up affiliations

\affiliations{
\item A. Kane (\url{adam.kane@ucc.ie}), University College Cork, Cooperage Building\, School of Biological 
Earth and Environmental Sciences\,Cork, Ireland.
\item K. Healy and A. Jackson, Trinity College Dublin, Department of Zoology;
School of Natural Sciences, Dublin Ireland.
\item T. Guillerme, Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, UK.
%TG: hehehe!
\item G. Ruxton, School of Biology, Sir Harold Mitchell Building, Greenside Place, St Andrews, KY16 9TH,
United Kingdom
}

>>>>

\affiliations{
\item A. Kane (\url{adam.kane@ucc.ie}), University College Cork, Cooperage Building, School of Biological Earth and Environmental Sciences, Cork, Ireland.
\item K. Healy and A. Jackson, Trinity College Dublin, Department of Zoology, School of Natural Sciences, Dublin Ireland.
\item T. Guillerme, Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.
\item G. Ruxton, School of Biology, Sir Harold Mitchell Building, Greenside Place, St Andrews, KY16 9TH, United Kingdom.
}
